Exploring and understanding the Interdependence of Collaboration Networks

### 2018-08-22 draft.tex
edit2 draft files

\subsubsection{Co-author but do not cite:}
For all pairs in Distance matrix (considering only the upper diagonal) at time t $D(t)$ we count pairs $N^D$ with  $D_{ij} = 1$. Among the pairs $N^D$ we count pairs $N^D_{(C_{ij} + C_{ji}=0)}$

@@

\begin{figure*}[htbp]  
	\centering
	\includegraphics[scale = 0.33]{plots/d_m_1990}
	\includegraphics[scale = 0.33]{plots/d_m_2000}
	\includegraphics[scale = 0.33]{plots/d_m_2013}

@@

  \captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
  \caption{Distance Matrices for the years 1990,2000 and 2013 from top left to right. As the network evolves the color gradient represents the distribution of distances in co-authorship network at the given time. The bottom panel plot the distribution ratios of distanes $d_{ij}$ between pairs for the years 1990,2000 and 2013 (left to right)}
  \label{f2}
\end{figure*}
In Fig.\ref{f2} the spread in distance matrices(top panel) is proportional to the network size. Distribution of distances in the network as it  evolves shows the increased connectivity between authors at different distances. Pairs that have no existing path have been excluded in the above graphs. The d value for the peak of the distribution(5 in the final graph) and the spread from the mean(variance) decreases as the network evolves with time. The decreasing values for the peak and variance are due to the increase in connectivity of the network.

@@

	\includegraphics[scale = 0.55]{plots/fig1}

\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
\caption{Total number of citations between pairs of authors VS distance D between pairs in the co-authorship network(for all years till 2013)}
   \label{f3}
\end{figure}

@@

	\caption{Change in the number of citations exchanged between pair ij at distance D with time}
	\label{f3a}
\end{figure*}

The number of citations exchanged by pairs ij of authors at distance d apart in the co-authorship network for a time t falls almost exponentially as in Fig\ref{f3}. We ignore the citation exchanged between pairs that have no path in between.(Reason of doing this? Maybe because we are only interested in seeing the change in citations with your near or distant collaborators).

Another way to look at the same is to measure the rate of change of citations exchanged between ij pairs at a distance d for the time series data Fig\ref{f3a}. We notice that for direct collaborations(co-authorship events) the rate of citations exchanged increase with time with a sudden transition post 1995 which is also true for average degree of nodes as shown in figure. However the growth rate falls rapidly for distance 2 between pairs and is almost zero for distance 3 and higher. {\color{blue}This means that the citations exchange between ij pairs far in the co-authorship network could be considered as random.}

The change in the strength of collaboration between two authors i and j can be seen in fig\ref{f4}. Here the strength of collaboration is indicated by the total citations exchanged by i and j in that time period through their papers. This includes cases where i and j cite there previously written paper. For our case this adds to the strength.

@@

\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
\caption{Distribution of citations exchanged before and after Time of first co-authorship event between authors. The sudden peak and rise is an interesting observation specially the decay part.}
   \label{f4}
\end{figure*}

@@

@@

>>>>

\subsubsection{Co-author but do not cite:}
For all pairs in Distance matrix (considering only the upper diagonal) at time t $D(t)$ we count pairs $N^D$ with  $D_{ij} = 1$. Among the pairs $N^D$ we count pairs $N^D_{(C_{ij} + C_{ji}=0)}$
\begin{figure}
	\centering
	\includegraphics[scale = 0.45]{plots/d1_zcit}

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that co-author but do not cite each other.}
	\label{f2}
\end{figure}

@@

@@

  \captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
  \caption{The distribution ratios of distanes $d_{ij}$ between pairs for the years 1990,2000 and 2013 (left to right)}
  \label{f3}
\end{figure*}
In Fig.\ref{f3} the spread in distance matrices(top panel) is proportional to the network size. Distribution of distances in the network as it  evolves shows the increased connectivity between authors at different distances. Pairs that have no existing path have been excluded in the above graphs. The d value for the peak of the distribution(5 in the final graph) and the spread from the mean(variance) decreases as the network evolves with time. The decreasing values for the peak and variance are due to the increase in connectivity of the network.

@@

	\includegraphics[scale = 0.49]{plots/fig1}

\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
\caption{Total number of citations between pairs of authors VS distance D between pairs in the co-authorship network(for all years till 2013)}
   \label{f4}
\end{figure}

@@

	\caption{Change in the number of citations exchanged between pair ij at distance D with time}
	\label{f4a}
\end{figure*}

The number of citations exchanged by pairs ij of authors at distance d apart in the co-authorship network for a time t falls almost exponentially as in Fig\ref{f4}. We ignore the citation exchanged between pairs that have no path in between.(Reason of doing this? Maybe because we are only interested in seeing the change in citations with your near or distant collaborators).

Another way to look at the same is to measure the rate of change of citations exchanged between ij pairs at a distance d for the time series data Fig\ref{f4a}. We notice that for direct collaborations(co-authorship events) the rate of citations exchanged increase with time with a sudden transition post 1995 which is also true for average degree of nodes as shown in figure. However the growth rate falls rapidly for distance 2 between pairs and is almost zero for distance 3 and higher. {\color{blue}This means that the citations exchange between ij pairs far in the co-authorship network could be considered as random.}

The change in the strength of collaboration between two authors i and j can be seen in fig\ref{f5}. Here the strength of collaboration is indicated by the total citations exchanged by i and j in that time period through their papers. This includes cases where i and j cite there previously written paper. For our case this adds to the strength.

@@

@@

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Distribution of citations exchanged before and after Time of first co-authorship event between authors. The sudden peak and rise is an interesting observation specially the decay part.}
	\label{f6}
\end{figure*}

@@

\section{Conclusion}

\section{References}
